Quantifying and Modeling Global Water Accessibility including Water Typology

### 2021-01-20 docs/manuscript/manuscript.tex
correlation-basic figure 2 inserted.

Next, there were many missing values from the data. Therefore, we had to do a simple missing value analysis. We determined to avoid using water, transportation, or wealth variables which had greater than 50\% missing values. Ultimately, simplified data frame was 76 countries by 28 variables. After, two different tables are generated where one focused on the water accessibility variables and a explanatory variables. We selected 11 water accessibility variables based on the sources available such as location, time, and methodology \citep{price2019difference}. The water accessibility variable was organized
in the following table to allow for quick visualization for table 1. The other variables were used as an explanatory variables for determining the water accessibility predictors in Table 2. 
\begin{table}[h!]
  \centering
  \begin{tabular}{c c m{7cm}}\toprule
    \bf Variable & \bf Description & \bf Definition \\\midrule
    \texttt{ptap} & Households using a public tap/standpipe
 & Percentage of households whose main source of drinking water is a public tap/standpipe.
 \\\hline
 \texttt{bore} & Households using a tube well/borehole & Percentage of households whose main source of drinking water is a tube-well/borehole.
\\\hline
\texttt{pspr} & Households using a protected spring
& Percentage of households whose main source of drinking water is a protected spring.
\\\hline
\texttt{uspr} & Households using an unprotected spring
& Percentage of households whose main source of drinking water is an unprotected spring.
\\\hline
\texttt{pwel} & Households using a protected well
& Percentage of households whose main source of drinking water is a protected well.
\\\hline
\texttt{uwel} & Households using an unprotected well water
&Percentage of households whose main source of drinking water is an unprotected well.
\\\hline
\texttt{surw} & Households using surface water
& Percentage of households whose main source of drinking water is surface water.
\\\hline
\texttt{tles} & Households with water 30 minutes or less away round trip
&Percentage of households with water 30 minutes or less away round trip.
\\\hline 
\texttt{tmor} & Households with water more than 30 minutes away round trip & Percentage of households with water more than 30 minutes away round trip.
\\\hline
\texttt{rain} & Households using rainwater
& Percentage of households whose main source of drinking water is rainwater.
\\\hline
\texttt{phom} & Households using water piped into dwelling
&Percentage of households whose main source of drinking water is water piped into the dwelling.
\\\hline

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{year}
  \caption{Distribution of years of water accessibility variables}
  \label{fig:year}
\end{figure}
\subsection*{Model results}
First, we developed a correlation chart to quickly analyze if there is any great correlation between all the 28 numerical variables that may pertain to water accessibility.

begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{year}
  \caption{Distribution of years of water accessibility variables}
  \label{fig:year}
\end{figure}

>>>>

Next, there were many missing values from the data. Therefore, we had to do a simple missing value analysis. We determined to avoid using water, transportation, or wealth variables which had greater than 50\% missing values. Ultimately, simplified data frame was 76 countries by 28 variables. After, two different tables are generated where one focused on the water accessibility variables and a explanatory variables. We selected 11 water accessibility variables based on the sources available such as location, time, and methodology \citep{price2019difference}. The water accessibility variable was organized
in the following table to allow for quick visualization for table 1. The other variables were used as an explanatory variables for determining the water accessibility predictors in Table 2. 
\begin{table}[h!]
  \centering
  \begin{tabular}{c c m{5cm}}\toprule
    \bf Variable & \bf Description & \bf Definition \\\midrule
    \texttt{ptap} & Households using a public tap/standpipe
 & Percentage of households whose main source of drinking water is a public tap/standpipe.
 \\\hline
 \texttt{bore} & Households using a tube well/borehole & Percentage of households whose main source of drinking water is a tube-well/borehole.
\\\hline
\texttt{pspr} & Households using a protected spring
& Percentage of households whose main source of drinking water is a protected spring.
\\\hline
\texttt{uspr} & Households using an unprotected spring
& Percentage of households whose main source of drinking water is an unprotected spring.
\\\hline
\texttt{pwel} & Households using a protected well
& Percentage of households whose main source of drinking water is a protected well.
\\\hline
\texttt{uwel} & Households using an unprotected well water
&Percentage of households whose main source of drinking water is an unprotected well.
\\\hline
\texttt{surw} & Households using surface water
& Percentage of households whose main source of drinking water is surface water.
\\\hline
\texttt{tles} & Households with water 30 minutes or less away round trip
&Percentage of households with water 30 minutes or less away round trip.
\\\hline 
\texttt{tmor} & Households with water more than 30 minutes away round trip & Percentage of households with water more than 30 minutes away round trip.
\\\hline
\texttt{rain} & Households using rainwater
& Percentage of households whose main source of drinking water is rainwater.
\\\hline
\texttt{phom} & Households using water piped into dwelling
&Percentage of households whose main source of drinking water is water piped into the dwelling.
\\\hline

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{year}
  \caption{Distribution of years of water accessibility variables}
  \label{fig:year}
\end{figure}
\subsection*{Model results}
First, we developed a correlation chart to quickly analyze if there is any great correlation between all the 28 numerical variables that may pertain to water accessibility. We recognized the strong and weak relationship by the size and color of the correlation plot is shown in Figure 2, which indicates households with limited water service (liws) has strongest and positive relationship with Households possessing a bicycle (bicy). Meanwhile, households using an improved water source (imws) has the strongest and negative relationship with households using an unimproved water source (uiws). This initial finding results indicated that the initial variables are logical and can give us insight into further understanding and relationship between these variables.

\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{correlation-basic}
  \caption{Correlation graph of numerical variables}
  \label{fig:year}
\end{figure}
